---
title: "Exploring social media analytics with R"
author: "[Maria Prokofieva](https://github.com/mariaprokofieva)"
date: "02/12/2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE,echo=FALSE}
library(knitr)
#library(magick)
# Chunk options
knitr::opts_chunk$set(fig.width=7,echo=TRUE, fig.height=7, warning=FALSE, message=FALSE,prompt=T,tidy=T,include=TRUE,cache=TRUE,fig.align='center',fig.asp=0.50,opts.label ="squarefigure",cache = TRUE)
library(png)
library(grid)
```

Social media analytics (SMA) is a powerful tool that offer wide opportunities for academics and industry professionals. SMA relates to a number of tools to collect data from digital media platforms, process it into structured insights and assist in more information-driven decision making. The tutorial introduces SMA with R.


### Topics covered during the tutorial include:


* Benefits and challenges working with social media data (textual/non-textual information, large data volume, API access)

* Structure of the social media data (e.g. user-related data, posting related data, hashtags)

* Connecting to a social media platform (e.g. authentication) and downloading data 

  [Setting up API access for Twitter] (# setup-API)
  
  [Connecting to Twitter from R](#connect)
  
  [Downloading tweets with `twitterR`] (# downloading-tweets)


* Data analysis of the profile information (e.g. followers, likes, dislikes, favorites - platform dependent)
  [Analyse tweets] (# analyse-tweets)

* Data analysis of textual information and non-textual (e.g. user posts, comments, dynamics, sentiment analysis, word clouds, etc.)
  [Analyse text tweets] (# analyse-text)

* Visualisation of the social media data
______

### Resource:
* [Packages to be used - please install] 

```{r eval=FALSE}
install.packages("rtweet")
install.packages("wordcloud2")
install.packages("tidyverse")
install.packages("tidytext")
```

* Reference material

[Setting up the Twitter R package for text analytics](https://www.r-bloggers.com/setting-up-the-twitter-r-package-for-text-analytics/)

[Setting API for rtweet](https://rtweet.info/articles/auth.html)



________




* R and RStudio installation

R is a free software environment for data analysis and visualisation. It runs on a variety of platforms, including Windows and MacOS. You can download R for your computer 

[for Windows](https://cran.r-project.org/bin/windows/base/)

[for MacOS](https://cran.r-project.org/bin/windows/base/)

Once R is installed, please install RStudio [here](https://www.rstudio.com/products/rstudio/download/) - use RStudio Desktop Open Source License

The installation is very straightforward, but you can also have a look at these tutorials

[install R for Windows](https://www.youtube.com/watch?v=Ohnk9hcxf9M)

[install R for Mac](https://www.youtube.com/watch?v=uxuuWXU-7UQ)

___


# Connecting to Twitter from R {#connect}

Before you start working with Twitter in R, you need to setup your access in the Twitter itself. Please see [Setting up API in Twitter](twitterAPI.Rmd)


There are two main R packaages to work with Twitter:

* [`rtweet`](https://cran.r-project.org/web/packages/rtweet/index.html) 
* [`twitteR`](https://cran.r-project.org/web/packages/twitteR/README.html)

In this tutorial we will be using `rtweet`

To use this package you need to install it in R first. You do it by typing the following line 

```{r eval=FALSE}
install.packages("rtweet")
```

and then load this package
```{r eval=FALSE}
library(rtweet)
```
Now you are all ready to 




# whatever name you assigned to your created app
appname <- "MariaP"

## api key (example below is not a real key)
key <- "W6G8J2SOcOpoLnidoCeM4XIIH"

## api secret (example below is not a real key)
secret <- "MHdYH2ui7cQlsXoDVk65H6gnWyqolDuyaukfJIm4Vh8Su9rnoS"

# create token named "twitter_token"
twitter_token <- create_token(
  app = appname,
  consumer_key = key,
  consumer_secret = secret)


rt <- search_tweets(
  "@Crowdcube", n = 18000, include_rts = FALSE
)




