---
title: "Setting up API in Twitter"
author: "MariaProkofieva"
date: "02/12/2018"
output:
  html_document:
    self_contained: no
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
```{r include=FALSE,echo=FALSE}
library(knitr)
#library(magick)
knitr::opts_chunk$set(fig.width=7,echo=TRUE, fig.height=7, warning=FALSE, message=FALSE,prompt=T,tidy=T,include=TRUE,cache=TRUE,fig.align='center',fig.asp=0.50,opts.label ="squarefigure",cache = TRUE)
library(png)
library(grid)
```
### Resources
[FAQ Twitter Developer Account](https://developer.twitter.com/en/docs/accounts-and-users/subscribe-account-activity/FAQ.html)
[Setting API for rtweet](https://rtweet.info/articles/auth.html)

______

### Before you start
To connect to Twitter from R, you need to have a Twitter account. You can create it [here](https://twitter.com/signup) 
You need to note down your `username` and `password`

________


```{r echo=FALSE,fig.cap="Create a Twitter account at https://apps.twitter.com/."}
img <- readPNG(file.path("tutorial images/twitter1.png"))
grid.raster(img)
```


Now go to https://apps.twitter.com/ and sign in with your `username` and `password`

There you will need to set up your developer's access: click on `Apply for a developer account`

```{r echo=FALSE,fig.cap="Twitter Apps"}
img <- readPNG(file.path("tutorial images/dev1.png"))
grid.raster(img)
```

Select a Twitter username for which you are setting up your developer's access

```{r echo=FALSE}
img <- readPNG(file.path("tutorial images/dev2.png"))
grid.raster(img)
```

On the next screen select the option that better suit your needs, for our tutorial, we will be using option 2 `I am requesting access for my own personal use`

```{r echo=FALSE}
img <- readPNG(file.path("tutorial images/dev3.png"))
grid.raster(img)
```

Now you need to specify your application name and your country

```{r echo=FALSE}
img <- readPNG(file.path("tutorial images/dev4.png"))
grid.raster(img)
```

You will need to specify the case for your access (`Academic research` for me), write a 300 word description of your intended use and your relation to government entity

```{r echo=FALSE}
img <- readPNG(file.path("tutorial images/dev5.png"))
grid.raster(img)
```

For example, like this

```{r echo=FALSE}
img <- readPNG(file.path("tutorial images/dev6.png"))
grid.raster(img)
```

Now, you click submit and you will need to wait till Twitter approves your access

```{r echo=FALSE}
img <- readPNG(file.path("tutorial images/dev7.png"))
grid.raster(img)
```
_______________

Once your access is approved, your Developer account will look like this

```{r echo=FALSE}
img <- readPNG(file.path("tutorial images/dev8.png"))
grid.raster(img)
```

and you can set up your Twitter app now by clicking on `Create an app`

```{r echo=FALSE}
img <- readPNG(file.path("tutorial images/dev9.png"))
grid.raster(img)
```

Enter the details for your application:

*`App name`

* `brief description` 

* `website`

* `callback URL`, please set to http://127.0.0.1:1410 

```{r echo=FALSE}
img <- readPNG(file.path("tutorial images/dev11.png"))
grid.raster(img)
```

Click on `Create a new App`

Go to the `Keys and Access Tokens` tab and click on `Create my access token`

```{r echo=FALSE}
img <- readPNG(file.path("tutorial images/dev12.png"))
grid.raster(img)
```

You need to write down (copy and paste!) the details of your access:

* API key

* API secret

* Token

* Token secret

```{r echo=FALSE,fig.cap="Create a Twitter app at https://apps.twitter.com/."}
img <- readPNG(file.path("tutorial images/twitter3.png"))
#grid.raster(img)
grid.raster(img)
```
and now you can go back to R and connect from R!

